Governing through patronage: the bargain for education in decentralized Brazil

### 2020-10-01 paper/paper.tex
fix

How can we intervene in this chain to improve the quality of public services? Previous studies have explored how political incentives can improve the quality of public goods provision. Some have focused on the direct link between political principal and bureaucratic agent: increasing political oversight over bureaucracies may improve public services \citep{gulzar_politicians_2017, raffler_does_2016}. Others have focused on the more indirect electoral accountability link binding politicians to voters, exploring how to strengthen it to induce changes  \citep{boas_electoral_2019, besley_political_2003} Whether explicitly or implicitly, these theories posit a unitary political actor who interacts with either the bureaucracy or the electorate. Yet in much of the developing world, these politicians do not govern alone: in fact, they are embedded in democratic institutions where multiplicity of elected officials and power-sharing arrangements dramatically reshape the institutional chain connecting politician to public service provision \citep{francois_how_2015}.

>>>>

How can we intervene in this chain to improve the quality of public services? Previous studies have explored how politicians' incentives can improve the quality of public goods provision. Some have focused on the direct link between the political principal and bureaucratic agent: increasing political oversight over bureaucracies may improve public services \citep{gulzar_politicians_2017, raffler_does_2016}. Others have focused on the more indirect electoral accountability link binding politicians to voters, exploring how to strengthen it to induce positive changes \citep{boas_electoral_2019, besley_political_2003} Whether explicitly or implicitly, these theories posit a unitary political actor who interacts with either the bureaucracy or the electorate. Yet in much of the developing world, these politicians do not govern alone: in fact, they are embedded in democratic institutions where multiplicity of elected officials and power-sharing arrangements dramatically reshape the institutional chain connecting politician to public service provision \citep{francois_how_2015}.
